\newpage

\section{FEASIBILITY STUDY}


\subsection{Economic Feasibility}
Given that the proposed ”EV Charge” system is based on a mobile application utilizing the MERN stack & flutter, we’ll leverage the advantages of these widely used open-source technologies. The MERN stack offers a seamless and cost-effective approach to building a dynamic and responsive application, ensuring a high-quality user experience while minimizing development expenses.The primary components of the MERN stack are well-established and supported by a large developer community. The use of opensource tools eliminates substantial licensing costs, making our project economically viable.

\subsection{Operational Feasibility}
\subsubsection{Scalability}
The MERN stack is highly scalable due to its distributed architecture, which allows for horizontal scaling of the application. MongoDB, the database used in the MERN stack, is also highly scalable, making it a good choice for applications that need to handle numerous users and requests.

\subsubsection{Availability}
The MERN stack is highly available, with Node.js and Express providing a robust
backend infrastructure and React providing a performant frontend. MongoDB
replicates data across multiple nodes to ensure that it is always available.

\subsubsection{Maintenance}
As MERN stack is open-source, there is a large community of developers who
contribute to the maintenance of this stack. So, regular maintenance is performed to various components of the stack.

\subsubsection{Security}
MongoDB provides robust security features, including authentication and access
control, and Node.js and Express provide middleware for adding security features to the application. So, MERN stack is generally considered to be secure.

\subsection{Technical Feasibility}
All the technologies used in our application like: React, Flutter, Express, Django, etc. are backed by big companies and have a huge community around it. So, it is always easy to get any technical support. So, the project is technically feasible.