\newpage

\section{LITERATURE REVIEW}
\subsection{Existing}
\begin{itemize}
    \item \textbf{NepEV:}
    
    NepEv is a mobile app which provides the information about EV charging stations in Nepal like location, distance, their capacity, and rates making the process of finding charging station faster than ever. \cite{Nep_EV}It used technologies such as Flutter, Android Studio, Firebase. It was promoted by hamrocars and many other online EV car content creators. It focused to provides booking capabilities for charging hubs, plan routes with EV stations into account.It has platform for various company charging station as well as minimizing hassle of travelling with EVs.
    
    \item \textbf{EV Charging Stations Nepal:}
    
    \cite{EV_App}An applicaiton for EV Charging stations in Nepal with interactive map system. The app listed the current Electric vehicle charging stations located in Nepal with the help of an interactive map system and an easy-to-view compiled list view with quick actions to help users get familiar with the charging station.
\end{itemize}

\newpage
\subsection{Proposed}
In this proposed project, we plan to build seamless integration of data from multiple sources, ensuring accurate, up-to-date information for users. The user can view EV charging station real time upto date information with real-time fuel station and repair garage location features. The user can compare as well as sort the stations on the basis of price, distance, type, cost and other quantity. We plan to capitalize on the MERN stack and flutter technologies, harnessing their advantages in creating a comprehensive and user-centric application. We hope that the completed app aspires to transform how individuals navigate, access, and engage with transportation services, contributing to a more sustainable and user-oriented transportation ecosystem.

\subsubsection{Functional Requirement}
Functional requirements are product features or functions that developers must implement to enable users to accomplish their tasks. They describe system behaviour under specific conditions. The functional requirements for my project are:
\begin{itemize}
    \item The app should be able to register new users and login already registered users.
    \item The app should allow users to view station details like: location, availability, charging rates, reviews, etc.
    \item Users should be able to search for nearby repair garages.
    \item Users should be able to book charging station.
    \item Admin should be allowded to manage charging station info.
\end{itemize}
\subsubsection{Non-Functional Requirement}
Non-functional requirements  are the set of specifications that describe the system's operation capabilities and constraints and attempt to improve it's functionality. The non-functional requirements required for our project are given below:
\begin{itemize}
    \item The app should be user friendly and easy to use.
    \item The app must have efficient throughput and response time.
    \item The app should provide accurate and up-to-date information about charging stations, fuel stations, and repair garages.
    \item User data, including personal information and payment details, should be securely stored and transmitted.
    \item The app's codebase should be well-organized and documented for easy maintenance and updates.
    \item The app should support multiple languages.
    \item The app should be available and accessible to users at all times.
\end{itemize}